visualFields 1.0.7: Tools for Analyzing the Field of Vision in \proglang{R}

### 2025-05-19 jss-article-rnw/article.Rnw
Added references.

In visual field testing, the observer either presses or does not press a button within a fixed time window following the presentation of a light increment in the visual field (a yes/no response). The relationship between stimulus strength and response probability is modeled by a psychometric function, which characterizes the likelihood of a "yes" response as a function of stimulus strength. These models yield an estimate of the threshold, defined as the stimulus strength at which the observer detects the stimulus with a probability of 50\%.

@@

To improve efficiency, adaptive algorithms have been developed to reduce the number of stimulus presentations with minimal compromise in accuracy. A commonly used example is the staircase algorithm, in which the stimulus intensity decreases after a "seen" response and increases after a "not seen" response. The step size is halved after each reversal (i.e., a change in response direction). More sophisticated algorithms balance precision and test duration, often incorporating information from adjacent locations in the visual field. A notable example is the Swedish Interactive Threshold Algorithm (SITA) used in the Humphrey Field Analyzer.

@@

$L_{max}$ may differ between parameter types, and the Humphrey Field Analyzer uses 10,000 asb, whereas recent Octopus 900 perimeters commonly use 4000 asb.

>>>>

In visual field testing, the observer either presses or does not press a button within a fixed time window following the presentation of a light increment in the visual field (a yes/no response). The relationship between stimulus strength and response probability is modeled by a \emph{psychometric function}, which characterizes the likelihood of a "yes" response as a function of stimulus strength \citep{CH:knoblauch_modeling_2012}. These models yield an estimate of the threshold, defined as the stimulus strength at which the observer detects the stimulus with a probability of 50\%.

@@

To improve efficiency, adaptive algorithms have been developed to reduce the number of stimulus presentations with minimal compromise in accuracy. A commonly used example is the staircase algorithm, in which the stimulus intensity decreases after a "seen" response and increases after a "not seen" response. The step size is halved after each reversal (i.e., a change in response direction). More sophisticated algorithms balance precision and test duration, often incorporating information from adjacent locations in the visual field. A notable example is the \emph{Swedish Interactive Threshold Algorithm (SITA)} used in the Humphrey Field Analyzer.

@@

$L_{max}$ may differ between parameter types, and the Humphrey Field Analyzer uses 10{,}000\,asb, whereas recent Octopus 900 perimeters commonly use 4000\,asb \citep{CH:racette_visual_nodate}.
